---
title: "Tarea_4_Ejercicio4"
author: "Elian Gonzalez Hernandez"
date: "12 de marzo de 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**a) Describe how the shared nearest neighbor algorithm groups vertices.**

$\\$

```{r}

# Initialize the SNN graph G with V(G) vertices and no edges

#     dado un vertice i
# 1:  foreach i = 1 to V (G) do

#     dado un vertice j
# 2:  foreach j = i + 1 to V (G) do

#     iniciamos un contador en 0
# 3:  counter = 0

#     para un vertice m que sea diferente de i e j
# 4:  foreach m = 1 to V (G) do

#     Condición: si el vértice i y el vértice j ambos tienen una arista con vértice m
# 5:  if vertex i and vertex j both have an edge with vertex m

#     Entonces: si se cumple la anterior condición se cuenta 1
# 6:  then
# 7:  counter = counter + 1
# 8:  end

#     Condición: si se cumple la condición de contador mayor o igual que k
# 9:  if counter >= k then

#     Entonces: conecte una arista entre el vértice i y el vértice j en G
# 10: Connect an edge between vertex i and vertex j in G
# 11: end
# 12: end
# 13: return G

```

$\\$
$\\$
$\\$
$\\$

**b) Based on your answer to part a, how many total nodes are required at minimum to find a pair of nodes with n shared nearest neighbors? Explain your answer.**

Como mínimo necesitaría n + 2 nodos.Esto es debido a que si queremos n nodos vecinos en común necesitamos una pareja de nodos (2 nodos) que tengan enlaces a estos vecinos.

$\\$
$\\$
$\\$
$\\$

**c) Given the list of vertices with x and y coordinates shown below, construct an adjacency matrix of the vertices,where vertices are considered to be neighbors (adjacent) if they are within a distance of 4, using Euclidean distance. Note, the vertices should not be considered adjacent to themselves.**

$\\$
$\\$
$\\$

```{r}

V = rbind(c(1,2),c(4,6),c(4,4),c(5,4),c(2,6),c(9,3),c(4,1),c(7,1),c(2,7),c(8,5))
rownames(V) = c("A","B","C","D","E","F","G","H","I","J")
colnames(V) = c("x","y")
A = matrix(0, nrow = 10, ncol = 10 )
rownames(A) = c("A","B","C","D","E","F","G","H","I","J")
colnames(A) = c("A","B","C","D","E","F","G","H","I","J")
for(idx in 1:10){
  for(jdx in 1:10){
    if(idx == jdx){
      A[idx,jdx] = 0
    }else{
      distancia = sqrt((V[jdx,2]-V[idx,2])^2)+((V[jdx,1]-V[idx,1])^2)
      if(distancia <= 4){
        A[idx,jdx]=1
      }else{
        A[idx,jdx]=0
      }
    }
  }
}

#adjacency matrix
A
```

$\\$

$\\$

$\\$

$\\$

**d) Using the adjacency matrix that you have created, find and list all the pairs of nodes that have at least two shared neighbors in common.**

```{r}
library(igraph)
# No pude utilizar la librería ‘ProximityMeasure’ porque no es compatible con mi versión de  R 3.4.3
# package ‘ProximityMeasure’ is not available (for R version 3.4.3)
# Por lo tanto mostraré el grafo y sacaré visualmente el listado de todos los pares de nodos que 
# tienen al menos dos vecinos compartidos.

plot(graph_from_adjacency_matrix(A, mode = "undirected"))
#Los pares de nodos que tienen al menos dos vecinos compartidos son C--D y B--G

```

$\\$
$\\$
$\\$

**e)  List all the pairs of nodes that have at least three shared neighbors in common.**

```{r}

# No pude utilizar la librería ‘ProximityMeasure’ porque no es compatible con mi versión de  R 3.4.3

# package ‘ProximityMeasure’ is not available (for R version 3.4.3)

# Por lo tanto mostraré el grafo y sacaré visualmente el listado de todos los pares 
# de nodos que tienen al menos tres vecinos compartidos.

plot(graph_from_adjacency_matrix(A, mode = "undirected"))
#Este grafo no tiene pares de nodos que tengan al menos tres vecinos compartidos.


```

